Data Preparation, Integration and Cleaning

### 2017-02-27 abbDataPrep_Script.Rmd
adding offline option

@@

@@

  str.data <- str.data[str.data$nightly.rate >= 50 &
                         str.data$med.rate <= 500, ]

@@

  ltr.data <- ltr.data[ltr.data$gross.revenue > 10000, ]

@@

Compute a full value of that total listing count

```{r and.bookings, message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE}

@@

>>>>

  offline <- TRUE

@@

  if(offline){

  source(paste0(code.path, '/dataVizTools/ggPlotTools.R'))
  source(paste0(code.path, '/datamgmttools/dataMungeTools.R'))
  source(paste0(code.path, '/spatialTools/spatialLogitModels.R'))
  source(paste0(code.path, '/spatialTools/point2surface_Tools.R'))

@@

  str.data <- str.data[str.data$med.rate >= 50 &
                         str.data$med.rate <= 500, ]

@@

  ltr.data <- ltr.data[ltr.data$dom <= 180, ]

@@

@@

  # Count Cleaning
  countCleaning('hostpolicy')
